\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-09 body.tex
Save.
Collect Typing Rules in One page.
Start Reworking Metatheory QIIT possibly removable altogether
compilation of family STLC
selected syntax
stuff
Start Canonicity/Consistency.
edits and tightening
sneak peek of linkage transformer use
Update Appendix.

% Macro for all use, the macro for metatheory syntax
\newcommand{\denotes}[1]{{\llbracket {#1} \rrbracket}}
\newcommand{\denotesS}[1]{{{\llbracket {#1} \rrbracket}_S}}
\newcommand{\goodCtx}[2]{{ {#1} \ \vdash }}
\newcommand{\goodType}[3]{{ {#1} \vdash {#2} }}
\newcommand{\goodTerm}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSub}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSig}[3]{{ {#1} \vdash {#2} \ \  Sig^{#3} }}
\newcommand{\goodWSig}[3]{{ {#1} \vdash {#2} \ \ WSig^{#3} }}
\newcommand{\goodSeal}[4]{{ {#1} \vdash {#2} : {#3} \  |\  {#4} }}
\newcommand{\goodInh}[4]{{ {#1} \vdash {#2} : {#3} \twoheadrightarrow {#4}}}
\newcommand{\nat}{\mathbf{N}}

\newcommand{\cU}{{\mathcal{U}}}
\newcommand{\cB}{{\mathbb{B}}}
\newcommand{\cL}{{\mathcal{L}}}
\newcommand{\cC}{{\mathcal{C}}}
\newcommand{\cCt}{{\mathcal{C}_t}}
\newcommand{\bW}{{\mathbb{W}}}

@@

\section{Prototypical Coq Implementation}
% we need to make this section before Metatheory
% because a lot of our formulation in the metatheory
%   is inspired by the implementation
\label{sec:coqimpl}
\input{coqimpl.tex}

\section{Metatheory}

\section{Example}\label{sec:coqexample}
\input{coq-example.tex}

@@

\section{Limitations and Conclusion}
\label{sec:conclusion}

It is hard to write modular, extensible code and proofs.
We have presented the first language design that

... make exciting directions for future work.

@@

For syntactic translation, please check \\ \href{https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing}{https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing}. This is the first QIIT-model we give. A QIIT-model can be consider as an arbitrary mapping from the QIIT data(our syntax in this case), also respecting the quotient(judgemental equality in this case). Here we use (a subpart of) QIIT data itself as the destination of the mapping.

@@

For canonicity model, please check \\ \href{https://drive.google.com/file/d/1R6C7QNfyu8fbl6LE2ruvpqZ_ZDSRVo0c/view?usp=sharing}{https://drive.google.com/file/d/1R6C7QNfyu8fbl6LE2ruvpqZ_ZDSRVo0c/view?usp=sharing}. This is mainly following \citet{coquand2018canonicity,sterling2019algebraic}, but we carried out our argument in a type-theortic framework.  We call it canonicity model to emphasize that it is a model used to prove canonicity, it is also called reducibility argument, as an instance of proof-relevant logical relation. This argument can be considered as a verbose/more concrete version of \citet{kaposi2019gluing}.

@@

>>>>

@@

\section{Compiling Family Polymorphism to Parameterized Modules}
% we need to make this section before Metatheory
% because a lot of our formulation in the metatheory
%   is inspired by the implementation
\label{sec:coqimpl}
\input{coqimpl.tex}

\section{\TT: A Core Dependent Type Theory}
\label{sec:metatheory2}
\input{metatheory-condensed.tex}

\section{Case Studies}
\label{sec:casestudies}
\input{casestudies.tex}

@@

\section{Conclusion}
\label{sec:conclusion}

\input{conclusion.tex}

@@

For syntactic translation, please check \\ \href{https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing}{https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing}. The syntactic translation here is to translate most of the novel feature introduced in this paper into a standard MLTT. 
The essence here is to translate linkage into a sigma type  with dependent function inside---and the dependent function is simulating the nature of ``late-binding'' of each field.

This is the first QIIT-model we give. A QIIT-model can be roughly consider as an arbitrary mapping from the QIIT data(our syntax in this case), also respecting the quotient(judgemental equality in this case). Here, the syntactic translation model is mapping to (a subpart of) the original QIIT data (itself).

@@

For canonicity model, please check \\ \href{https://drive.google.com/file/d/1R6C7QNfyu8fbl6LE2ruvpqZ_ZDSRVo0c/view?usp=sharing}{https://drive.google.com/file/d/1R6C7QNfyu8fbl6LE2ruvpqZ_ZDSRVo0c/view?usp=sharing}. This is mainly following \citet{coquand2018canonicity,sterling2019algebraic}, but we carried out our argument in a type-theortic framework.  In other references, it is also called reducibility argument, as an instance of proof-relevant logical relation. Our model can be considered as a verbose/more concrete version of \citet{kaposi2019gluing}.

For both consistency and canonicity model, the key part is still about handling the novel feature. Thanks to the insight from syntactic translation, we can always inspired by consistency and canonicity model of sigma type and dependent function in standard MLTT.

@@

\section{Typing Rules in one Figure}
\include{all-typing-rule.tex}

\section{Metatheory, in detail}

\section{Example in Metatheory}\label{sec:coqexample}
\input{coq-example.tex}
